\documentclass[../DoAn.tex]{subfiles}
\begin{document}

\begin{center}
    {\Large\textbf{ABSTRACT}}\\
\end{center}
\vspace{1cm}

Vietnamese is a tonal language with diacritics and many multi-word expressions. These characteristics make a Vietnamese crossword-style word puzzle game different from word puzzles that only use non-diacritic Latin characters. Within the scope of this thesis, several common crossword implementations do not focus on Vietnamese word normalization, space removal for board placement, diacritic-aware answer checking, topic organization, and local progress saving.

This thesis presents the design and implementation of a Vietnamese crossword-style word puzzle game built with the Godot engine. The vocabulary data is organized by topic and level. The system normalizes Vietnamese words for board generation, removes spaces when placing words on the puzzle grid, and still allows players to enter complete Vietnamese answers. The main features include automatic board generation, clue management, local player profiles, score calculation, star-based hints, and local progress saving.

The result is a playable prototype for personal computer use. At the functional level, the game supports vocabulary practice by asking players to read clues, connect meanings, and enter Vietnamese answers by topic. The main contribution of the thesis is a practical workflow for handling Vietnamese vocabulary in a crossword-style word puzzle game and integrating that workflow into a Godot-based application.

\begin{flushright}
Student\\
\begin{tabular}{@{}c@{}}
\textit{(Signature and full name)}
\end{tabular}
\end{flushright}

\end{document}
